An exact method for the multi-product p-batch processing time maximization problem

### 2023-10-10 manuscript/manuscript.tex
updating paper

\documentclass[authoryear,manuscript,12pt]{elsarticle}
\usepackage{setspace}
\doublespacing
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{rotating}
\usepackage{multirow}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

@@

\title{Exact method for the multi-product p-batch processing time maximization problem}

@@

Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: single unit, flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; 6) problem: design, planning, sizing, scheduling and/or balancing (with compatible or incompatible jobs); 7) restrictions: ; and 8) performance measure: makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and multiple criteria.

\begin{figure}[h]
\label{fig:taxonomy}
\begin{center}
\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]

\node[draw](SS){single stage};
\node[right=0.3cm of SS, draw](MS){multi-stage};
\node[draw,dashed,rounded corners,fit=(SS) (MS),inner sep=12pt,label={above:{number of stages}}](stages){};

\node[right=1.2cm of MS, draw](SP){single period};
\node[right=0.3cm of SP, draw](MP){multi-period};
\node[right=0.3cm of MP, draw](CP){cyclic};
\node[draw,dashed,rounded corners,fit=(SP) (MP) (CP),inner sep=12pt,label={above:{periods}}](periods){};

\node[below left=1.5cm and -1.2cm of stages.south east, draw](L2){flowshop};
\node[left=0.5cm of L2, draw](L1){single unit};
\node[right=0.5cm of L2, draw](L3){parallel};
\node[right=0.5cm of L3, draw](L4){networked};
\node[draw,dashed,rounded corners,fit=(L1) (L2) (L3) (L4),inner sep=15pt,label={west:\rotatebox{90}{layout}}](layout){};

\node[below left=1.5cm and 0cm of layout.south, draw](P3){sizing};
\node[left=0.5cm of P3, draw](P2){planning};
\node[left=0.5cm of P2, draw](P1){design};
\node[right=0.5cm of P3, draw](P4){scheduling};
\node[right=0.5cm of P4, draw](P5){balancing};
\node[draw,dashed,rounded corners,fit=(P1) (P2) (P3) (P4) (P5),inner sep=15pt,label={west:\rotatebox{90}{problem}}](problem){};

\node[below left=1.5cm and 0cm of problem.south, draw](O1){s-batch};
\node[right=0.5cm of O1, draw](O2){p-batch};
\node[draw,dashed,rounded corners,fit=(O1) (O2),inner sep=15pt,label={west:\rotatebox{90}{mode}}](mode){};

\node[below left=3.5cm and 6cm of mode.south, draw, rotate=90](M1){makespan};
\node[right=1cm of M1.south west, draw, rotate=90](M2){setup/holding cost};
\node[right=1cm of M2.south west, draw, rotate=90](M3){customer satisfaction};
\node[right=1cm of M3.south west, draw, rotate=90](M4){plant performance};
\node[draw,dashed,rounded corners,fit=(M1) (M2) (M3) (M4),inner sep=15pt,label={west:\rotatebox{90}{performance measure}}](measure){};

\node[right=2.5cm of M4.south west, draw, rotate=90](R1){family incompatibility};
\node[right=1cm of R1.south west, draw, rotate=90](R2){capacity constrained};
\node[right=1cm of R2.south west, draw, rotate=90](R3){color incompatibility};
\node[right=1cm of R3.south west, draw, rotate=90](R4){work-in-process storage};
\node[draw,dashed,rounded corners,fit=(R1) (R2) (R3) (R4),inner sep=15pt,label={west:\rotatebox{90}{restriction}}](restriction){};

\node[below right =1cm and 0cm of measure.south west](N1){};
\node[right =1cm of N1](N2){};
\draw[blue, very thick] (N1.east) -- (N2.west);

\node[right =0cm of N2](A1){\cite{Eilon1985}};
\draw[blue, very thick] (SS.south) -- (L1.north);
\draw[blue, very thick] (CP.south) -- (L1.north);
\draw[blue, very thick] (L1.south) -- (P4.north);
\draw[blue, very thick] (P4.south) -- (O1.north);
\draw[blue, very thick] (O1.south) -- (M2.east);

\node[right=4cm of N1](N3){};
\node[right =1cm of N3](N4){};
\draw[red, very thick] (N3.east) -- (N4.west);

\node[right =0cm of N4](A2){\cite{LiuEtAl2020}};
\draw[red, very thick] (MS.south) -- (L4.north);
\draw[red, very thick] (MP.south) -- (L4.north);
\draw[red, very thick] (L4.south) -- (P3.north);
\draw[red, very thick] (P3.south) -- (O1.north);

\node[below right =-2.5mm and 1mm of O1.south](N5){};
\node[above right =-2.5mm and -1.5mm of M2.east](N6){};

\draw[red, very thick] (N5) -- (N6);
\draw[red, very thick] (O1.south) -- (R2.east);
\draw[red, very thick] (O1.south) -- (R4.east);

\end{tikzpicture}
\end{center}
\caption{Taxonomy of multi-product batch problems cited in this paper.}
\end{figure}

>>>>

\documentclass[authoryear,manuscript,12pt]{elsarticle}
\usepackage{setspace}
\doublespacing
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{rotating}
\usepackage{multirow}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\usepackage{enumitem}

@@

\title{An exact method for the multi-product p-batch processing time maximization problem}

@@

\subsection{Taxonomy and notation}

In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:

\begin{enumerate}[label=\arabic*)]
\item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CN) and /or divergent (DN));
\item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
\item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
\item \textbf{planning horizon ($\eta$)}: single period (SP) or multiperiod (MP);
\item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
\item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
\item \textbf{performance measure ($\delta$)}: capital cost ($C$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
\item \textbf{restrictions ($\rho$)}: incompatible jobs (IJ).
\end{enumerate}

So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$. The multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab. .

\subsection{Contributions of this paper}
